\chapter{Introduction}
\label{chap:introduction}

Since the dawn of physics one of the most fundamental question has been to find the most elemental constituents of matter. In this regard the standard model has proven to be extremely useful. It postulates six quark species \{up, down, strange, charm, bottom, top\}, three charged kinds of leptons \{electron, muon, tau\}, a neutral neutrino for every charged lepton specie and four species of gauge bosons \{photon, $W$, $Z$, gluon\} as well as the Higgs boson $H$. Besides its achievement in describing the very basic principals of interactions and its experimental predictions being very precise, there emerged significant flaws; namely the high energy limit, matter \& anti-matter asymmetry and the existence of dark matter.

The Belle~\RN{2} experiment was designed to aid in the search for new physics phenomena with a massive volume of data in the flavour sector. The violation of $CP$-symmetry has already been observed at the predecessor experiment Belle. However, analysis of rare decays with only small standard model corrections are hard to spot and require more statistics. At the hardware frontier the detector and accelerator system was updated. The software side on the other hand required adaption as well to cope with the amount of data to be produced.

In order to spot such small deviations in such large sets of data, a reliable particle identification is a fundamental requirement. Its role is to assign labels of particle species to tracks which are identified by the detector system. By doing so, it allows further analysis of events to only select the particles relevant to them.

